Comparing the Efficiency of Machine Learning and Deep Learning Models in Source Code Authorship Attribution

### 2025-03-02 article.tex
fixed bug of dottted line

\addplot3+[
    mark=none,
    blue,
    dotted,
    line width=1pt,
    nodes near coords,
    every node near coord/.append style={
        mark=none,
        fill=none,
        draw=none,
        text=black,
        font=\scriptsize,
        yshift=0pt
    }
] coordinates {
    (0.8,4,85.84) (0.8,3,80.56) (0.8,2,70.60) (0.8,1,66.24) % Coordinates are adjusted to match the reversed ytick
};

@@

\addplot3+[ybar, bar width=12pt, fill=blue, draw=none, bar shift=-0.2]
    coordinates {(3,4,83.72) (3,3,40.62) (3,2,35.66) (3,1,24.07)}; % Coordinates are adjusted to match the reversed ytick
\addplot3+[ybar, bar width=12pt, fill=red, draw=none, bar shift=0]
    coordinates {(3,4,84.72) (3,3,40.53) (3,2,36.41) (3,1,27.40)}; % Coordinates are adjusted to match the reversed ytick
\addplot3+[ybar, bar width=12pt, fill=brown, draw=none, bar shift=+0.2]
    coordinates {(3,4,82.58) (3,3,38.30) (3,2,33.93) (3,1,23.33)}; % Coordinates are adjusted to match the reversed ytick

\addplot3+[
    mark=none,
    blue,
    dotted,
    line width=1pt,
    nodes near coords,
    every node near coord/.append style={
        mark=none,
        fill=none,
        draw=none,
        text=black,
        font=\scriptsize,
        yshift=0pt
    }
] coordinates {
    (2.8,4,83.72) (2.8,3,40.62) (2.8,2,35.66) (2.8,1,24.07) % Coordinates are adjusted to match the reversed ytick
};

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{example-image} % Uses the default dummy image provided by the graphicx package
\caption{A sample figure using the default example image.}
\end{figure}

>>>>

    %dotted line
\addplot3+[
    mark=none,
    blue,
    dotted,
    line width=1pt,
    nodes near coords,
    every node near coord/.append style={
        mark=none,
        fill=none,
        draw=none,
        text=black,
        font=\scriptsize,
        yshift=0pt
    }
] coordinates {
    (0.8,4,85.84) (0.8,3,80.56) (0.8,2,70.60) (0.8,1,66.24) % Coordinates are adjusted to match the reversed ytick
};

@@

\addplot3+[ybar, bar width=12pt, fill=blue, draw=none, bar shift=-0.2]
    coordinates {(3,4,83.72) (3,3,40.62) (3,2,35.66) (3,1,24.07)}; % Coordinates are adjusted to match the reversed ytick
\addplot3+[ybar, bar width=12pt, fill=red, draw=none, bar shift=0]
    coordinates {(3,4,84.72) (3,3,40.53) (3,2,36.41) (3,1,27.40)}; % Coordinates are adjusted to match the reversed ytick
\addplot3+[ybar, bar width=12pt, fill=brown, draw=none, bar shift=+0.2]
    coordinates {(3,4,82.58) (3,3,38.30) (3,2,33.93) (3,1,23.33)}; % Coordinates are adjusted to match the reversed ytick
\foreach \yA/\zA/\yB/\zB in {
    4/83.72/3/40.62,
    3/40.62/2/35.66,
    2/35.66/1/24.07
} {
    \addplot3+[
        mark=none,
        blue,
        dotted,
        line width=1pt,
        nodes near coords,
        every node near coord/.append style={
            mark=none,
            fill=none,
            draw=none,
            text=black,
            font=\scriptsize,
            yshift=0pt
        }
    ] coordinates {
        (3,\yA,\zA) (3,\yB,\zB)
    };
}

@@
